Change in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2019-12-04 analysis/paper/paper.Rmd
Trying to convert the codes working with google sheet to codes with xlxs

@@

Artifact density and retouch <- maybe we need to add the result of retouch, separately 
We use the combination of the artifact density and retouch frequency as a proxy to identify the mobility and residential pattern of hunter-gatherers. The result shows that there is no clear pattern during the transition period and then it became more expedient at the end of the transition (Fig 5. The combination of artifact density and retouch). That is to say, the hunter-gatherer became either more residential or the majority of the site that this research studies were used as base camps or residence rather than shortly occupied camps for certain tasks.

@@

ggplot(kasa_long, 
       aes(age_ka, 
           percentage,
           fill = artefact_type)) +
  geom_col() +
  ylab("Percentage") +
  xlab("Age of assemblage (ka)") +
  labs(fill="Artifact type")+
  theme_minimal(base_size = 16)

@@

>>>>

# without site name
ggplot(kasv_tidy,
       aes(date_age / 1000,
           artefact_density)) +
  geom_point(aes(size = total_artifacts)) +
  ylab("Artefact density") +
  xlab("Age of assemblage (ka)") + 
  scale_size_continuous(name = "Total number\nof artifacts")  +
  theme_minimal(base_size = 16)
ggsave("figures/age-by-density.png")

@@

ggplot(kasa_long, 
       aes(age_ka, 
           percentage,
           fill = artefact_type)) +
  geom_col(position = "fill") +
  ylab("Percentage") +
  xlab("Age of assemblage (ka)") +
    scale_fill_viridis_d(name = "Artifact type",
                       option = "D") +
  coord_flip() +
  theme_minimal(base_size = 16)

# comparable figure to the raw material one (BM created)

kasa_long1 <-
  kasa %>%
  gather(site, 
         count, 
         -X) %>% 
  filter(!is.na(count)) %>% 
  group_by(site) %>% 
   mutate(percentage = count / sum(count, na.rm = TRUE) * 100,
         total = sum(count, na.rm = TRUE)) %>% 
  filter(!is.na(percentage)) %>% 
  # if percentage is <10%, call it 'other'
  mutate(artefact_type = ifelse(as.character(X) == 'stemmed_point',
                                'stemmed_point', 
                                ifelse(percentage >= 10 | X == "unkown", 
                                as.character(X), "other_tools"))) %>% 
  mutate(axis_label = glue('{site}\n(n = {total})'))  %>% 
  select(-X)
  # join to get ages of the sites
kasa_long2 <- 
kasa_long1 %>% 
  group_by(site, 
           artefact_type) %>% 
  summarise(percentage = sum(percentage)) %>% 
  left_join(mydata_ages, 
            by = c('site' = 'site_name')) %>% 
  arrange(age_ka) %>% 
  distinct(.keep_all = TRUE) %>%
  filter(!is.na(age_ka)) %>% 
  mutate(axis_label = glue('{site} ({round(age_ka,1)} ka)'))

ggplot(kasa_long2, 
       aes(
           reorder(axis_label, -age_ka),
           percentage,
           fill = artefact_type)) +
  geom_col(position = "fill") +
  ylab("Percentage") +
   xlab("Assemblage (youngest at the top)") +
  theme_minimal(base_size = 16)  +
    scale_fill_viridis_d(name = "Artefact type",
                       option = "D") +
  coord_flip() +
  theme_minimal(base_size = 12) 
ggsave("figures/artefact-types.png")

```
Artifact density and retouch <- maybe we need to add the result of retouch, separately 
We use the combination of the artifact density and retouch frequency as a proxy to identify the mobility and residential pattern of hunter-gatherers. The result shows that there is no clear pattern during the transition period and then it became more expedient at the end of the transition (Fig 5. The combination of artifact density and retouch). That is to say, the hunter-gatherer became either more residential or the majority of the site that this research studies were used as base camps or residence rather than shortly occupied camps for certain tasks.

@@

@@

```{r}

# try not to use googlesheet and make the upper chunck work

library(readxl)
path <- "analysis/data/raw_data/Overall_info.xlsx"
excel_sheets(path = path)

p_sheets <- c("general_info" ,"assemblage_info")

k_kas_sites_sheets <- map(p_sheets, ~path %>% )
